---
title: "Project 1"
output:
  html_document:
    df_print: paged
  word_document: default
  html_notebook: default
---

**Data Set**
    The data set chosen has been taken from Kaggle: https://www.kaggle.com/datasets/souvikahmed071/social-media-and-mental-health
    This is significant data to inspect because media usage is a big part of everyones life and it's important to see the effect it may have on                different groups of people.

```{r}
library(yarrr)
library(readr)
library(mosaic)
library(tibble)
```
```{r}
sm <- (smmh) %>% na.omit()
sm
```
```{r}
sm <- sm %>% mutate(gender = sm$`2. Gender`, age = sm$`1. What is your age?`, status = sm$`3. Relationship Status`, occupation = sm$`4. Occupation Status`, media = sm$`6. Do you use social media?`, schoolType = sm$`5. What type of organizations are you affiliated with?`, avg_time = sm$`8. What is the average time you spend on social media every day?`, specific = sm$`9. How often do you find yourself using Social media without a specific purpose?` ) %>%
            select(gender, age, status, occupation, media, schoolType, avg_time, specific)
sm #Here I have chosen to rename the columns for easier access
```
```{r}
sm <- sm %>% mutate(gender_new = factor(case_when(gender == "Male" ~ 'male',
                                                          gender == "Female" ~ 'female',
                                                              gender != "female" ~ 'other',
                                                                  gender != "male" ~ 'other')))
sm 
```
```{r}
sm <- sm %>% mutate(status_new = factor(case_when(status == "Single" ~ 'single',
                                                          status == "Divorced" ~ 'single',
                                                              gender != "Divorced" ~ 'taken',
                                                                  gender != "Single" ~ 'taken')))
sm #I have created two new columns so that I can work with a smaller amount of options to use in an interaction
```
```{r}
sm_int <- sm %>% mutate(group = interaction(gender_new, status_new, media))
sm_int #Here is a categorical variable with two values
```
```{r}
pirateplot( specific ~ group, data = sm_int) #Most of what we will be observing are groups that do have a form of media because most people in this data set have marked yes
```
```{r}
lm <- lm(specific ~ group, data=sm_int)
anova(lm)
```
**Results**
  The code above shows an anova test that has been done with a categorical variable named group that consists of the values: gender, relationship status and if they consume media. The specific column refers to how many hours they consume media. We are testing to see if...
  Null Hypothesis: There is no significant difference between the specific amount of hours of media consumed to at least one of the values in group.
  Alternative Hypothesis: There is a significant difference between the specific amount of hours of media consumed to at least on of the values in group.
  We concluded with a p-value < 0.05 so we accept our Null Hypothesis and reject the Alternative.
    
    
    
    
  **Non-Parametric Version to confirm results:**
```{r}
N <- 1000
Tstar <- matrix(NA, nrow = N)
for (b in (1:N)){ #We are shuffling the group to the specific variable and producing a result of each anova test result 1000 times
  Tstar[b] <- anova(lm(specific ~ shuffle(group), data=sm_int))[1,4]
}
```
```{r}
tibble(Tstar) %>% ggplot(aes(x = Tstar)) + 
  geom_histogram(aes(y = ..ncount..), bins=25, col=1, fill='orange') + 
  geom_vline(xintercept = c(0.4402095 , 1.7128723 ), col="blue", lwd=2) 
```
```{r}
 1 - pdata(Tstar, 0.04406)
```
```{r}
quantile(Tstar, c(0.1, 0.9) ) #Our 90 percentile confidence interval numbers which is plugged into the bar graph above
```